Probability

### 2016-04-19 prob.tex
fixed prob space

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
\def\C{{\mathbb{C}}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}

@@

Consider the two-qubit Hilbert space with computational basis
$\ket{0}$ and $\ket{1}$ and states:
\[
\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}, \qquad\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}\,.
\]
A possible space of events is the set
$\{ \mathbb{0}, \proj{0}, \proj{1}, \mathbb{1}\}$ consisting of the
projection operators $\proj{0}$ and $\proj{1}$ as well as the empty
projection $\mathbb{0}$ and the unit projection
$\mathbb{1} = \proj{0}+\proj{1}$. Each event is interpreted as a
possible post-measurement state of a quantum system as follows: given some
arbitrary current quantum $\ket{\psi}$ to be measured, the event
$\proj{0}$ states that the post-measurement state will be $\ket{0}$;
the event $\proj{1}$ states that the post-measurement state will be
$\ket{1}$; the event $\mathbb{1}$ states that the post-measurement
state will be a linear combination of $\ket{0}$ and $\ket{1}$; and the
event $\mathbb{0}$ states that the post-measurement state will be the
empty state. \\
\yutsung{How about replacing the above sentence by something like: 
\begin{quote}
Each event is interpreted as a possible post-measurement state of
a quantum system if that event occurs as follows~\cite{Abramsky2013}:
...... and the event $\mathbb{0}$ does not to state the post-measurement
state because it never occurs. 
\end{quote}
}\\
Clearly irrespective of the current state $\ket{\psi}$
and irrespective of the particular experiment, the probability of
event $\mathbb{0}$ will always be 0 (it is an impossible event) and
the probability of event $\mathbb{1}$ will always be 1 (it is a
certain event). The probabilities attached to other events will depend
on the particular state in question. If the state is $\ket{0}$, the
probability of event $\proj{0}$ is 1 and the probability of event
$\proj{1}$ is 0. If the state is $\ket{\ps}$, the probability of both
events $\proj{0}$ and $\proj{1}$ will be $\frac{1}{2}$. The same
Hilbert space setup admits other possible spaces of events. For
example, another space of events could be
$\{ \mathbb{0}, \proj{\ps}, \proj{\ms}, \mathbb{1}\}$. Using that
space of events, the state $\ket{0}$ maps both events $\proj{\ps}$ and
$\proj{\ms}$ to the probability $\frac{1}{2}$.

@@

We now formalize a \emph{quantum probability space} as
follows~\cite{Maassen2010,Swart2013}. We first assume an ambient
Hilbert space~$\Hilb$ and define the set of events $\qevents$ as all
linear combinations of \emph{projections} on~$\Hilb$. Specifically,
let $P_1, P_2, \ldots, P_k$ be mutually orthogonal projections on
$\Hilb$ with sum $\mathbb{1}$ and define the event space $\qevents$ to
be the linear span of these operators:
\[
\qevents=\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} .
\]
Each quantum state $\ket{\psi}$ induces a probability measure
$\mu_\psi : \qevents \rightarrow [0,1]$ on the space of events
defined as follows:
\[
\mu_\psi(A) = \ip{\psi}{A\psi}
\]
Similarly to the classical case, this probability measure satisfies: 
\begin{itemize}
\item $\mu(\mathbb{1})=1$, and 
\item for all $A\in\qevents$, we have $\mu(A^{*}A)\geq0$. 
\end{itemize}
\yutsung{The following is the diagram for quantum probability objects
and their corresponding physical meaning (in parentheses):
\[
\xymatrix{\textrm{projections (\textrm{events})}\ar[d]^{\mu_{\psi}\textrm{(probability)}} & \subsetneq & \textrm{Hermitian operators (observables)}\ar[d]^{\mu_{\psi}\textrm{(expectation value)}} & \subsetneq & \textrm{all operators in a }*\textrm{-algebra(?)}\ar[d]^{\mu_{\psi}\textrm{(?)}}\\
\left[0,1\right] & \subsetneq & \mathbb{R} & \subsetneq & \mathbb{C}
}
\]
Although the above paragraph claimed $\qevents$ is a set of events,
``all linear combinations of \emph{projections}'' and $\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} $
gives all operators in a $*$-algebra. Therefore, I got confused you
want $\qevents$ be ``the set of all events'' or ``the set of all
operators in a $*$-algebra''...}

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
\def\C{{\mathbb{C}}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}

@@

Consider the two-qubit Hilbert space with computational basis
$\ket{0}$ and $\ket{1}$ and states:
\[
\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}, \qquad\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}\,.
\]
The set of events associated with this Hilbert space consists of all
projections including the empty projection $\mathbb{0}$ and the unit
projection $\mathbb{1} = \proj{0}+\proj{1}$:
\[ 
\{ \mathbb{0}, \proj{0}, \proj{1}, \proj{\ps}, \proj{\ms}, \ldots, \mathbb{1}\}
\]
Each event is interpreted as a possible post post-measurement state of
a quantum system as follows: given some arbitrary current quantum
$\ket{\psi}$ to be measured, the event $\proj{0}$ states that the
post-measurement state will be $\ket{0}$; the event $\proj{1}$ states
that the post-measurement state will be $\ket{1}$; the event
$\proj{\ps}$ states that the post-measurement state will be
$\ket{\ps}$; the event $\proj{\ms}$ states that the post-measurement
state will be $\ket{\ms}$; the event $\mathbb{1}$ states that the
post-measurement state will be a linear combination of $\ket{0}$ and
$\ket{1}$; and the event $\mathbb{0}$ states that the post-measurement
state will be the empty state.

Clearly irrespective of the current state $\ket{\psi}$ and
irrespective of the particular experiment, the probability of event
$\mathbb{0}$ will always be 0 (it is an impossible event) and the
probability of event $\mathbb{1}$ will always be 1 (it is a certain
event). The probabilities attached to other events will depend on the
particular state in question. If the state is $\ket{0}$, the
probability of event $\proj{0}$ is 1; the probability of event
$\proj{1}$ is 0; the probability of event $\proj{\ps}$ is
$\frac{1}{2}$; and the probability of event $\proj{\ms}$ is
$\frac{1}{2}$. If the state is $\ket{\ps}$, the probability of both
events $\proj{0}$ and $\proj{1}$ will be $\frac{1}{2}$; the
probability of event $\proj{\ps}$ is 1; and the probability of event
$\proj{\ms}$ is 0.

@@

We now formalize a \emph{quantum probability space} as
follows~\cite{Maassen2010,Swart2013}. We first assume an ambient
Hilbert space~$\Hilb$ and define the set of events $\qevents$ as all
\emph{projections} on~$\Hilb$. Each quantum state $\ket{\psi}$ induces
a probability measure $\mu_\psi : \qevents \rightarrow [0,1]$ on the
space of events defined as follows:
\[
\mu_\psi(A) = \ip{\psi}{A\psi}
\]
Similarly to the classical case, this probability measure must satisfy:
\begin{itemize}
\item $\mu(\mathbb{1})=1$, and 
\item for a collection of pairwise orthogonal $A_i$, we have
  $\mu(\sum_i A_i) = \sum_i \mu(A_i)$.

\amr{CHECK because sum of
    projections may not be a projection}
\end{itemize}

\yutsung{The following is the diagram for quantum probability objects
and their corresponding physical meaning (in parentheses):
\[
\xymatrix{\textrm{projections (\textrm{events})}\ar[d]^{\mu_{\psi}\textrm{(probability)}} & \subsetneq & \textrm{Hermitian operators (observables)}\ar[d]^{\mu_{\psi}\textrm{(expectation value)}} & \subsetneq & \textrm{all operators in a }*\textrm{-algebra(?)}\ar[d]^{\mu_{\psi}\textrm{(?)}}\\
\left[0,1\right] & \subsetneq & \mathbb{R} & \subsetneq & \mathbb{C}
}
\]
Although the above paragraph claimed $\qevents$ is a set of events,
``all linear combinations of \emph{projections}'' and $\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} $
gives all operators in a $*$-algebra. Therefore, I got confused you
want $\qevents$ be ``the set of all events'' or ``the set of all
operators in a $*$-algebra''...}
